Information from Language Program Qualtrics Survey

### 2022-11-05 docs/draft/draft.Rmd
Update draft.Rmd

Several studies have analyzed online vs f2f.  general tendency says XX
Sangmin-Michelle (2020) students perceive online education as less effective
Ruiz-Aloson-Bartol et all (2022) Students had the belief that learnt less that what they could have learnt in a traditional face to face class. Este paper cita bastantes estudios viejos donde encuentran que la educación online tiene ventajas. Son todo papers pre-pandemic.

>>>>

Several studies have analyzed online vs f2f.  general tendency says XX
Sangmin-Michelle (2020) students perceive online education as less effective, 
Alhamami (2022) found a more positive attitude toward face-to-face enviroments in comparison to online class. 
Ruiz-Aloson-Bartol et all (2022) Students had the belief that learnt less that what they could have learnt in a traditional face to face class. Este paper cita bastantes estudios viejos donde encuentran que la educación online tiene ventajas. Son todo papers pre-pandemic.
